% !TeX root=../main.tex

\chapter{مجوعه پرامپتهای ساخت مجموعه داده}
\label{app:naturalDiscussionTemplate}

\thispagestyle{empty}



لیستی ۱۰۰ الگوی پیش‌فرض برای ایجاد تعاملات طبیعی و سازنده بین کاربران و سیستم  به شرح زیر است.

در ادامه 50 قالب مختلف برای پرسش آورده شده است.

\begin{LTR}
\begin{itemize}
\item    
"Hey, I loved '{movie}'. Any other {genere} films?",
\item
"Looking for movies like '{movie}' in the {genere} genre?",
\item
"Have you checked out anything like '{movie}' before? Maybe in the {genere} category?",
\item
"In the mood for {genere} movies similar to '{movie}'?",
\item
"What's your take on {genere} films akin to '{movie}'?",
\item
"Any movies in {genere} genre similar to '{movie}' that you recommend?",
\item
"Seen anything like '{movie}' recently? Perhaps in the {genere} category?",
\item
"Want recommendations for {genere} movies like '{movie}'?",
\item
"Searching for {genere} movies reminiscent of '{movie}'?",
\item
"What do you think about exploring {genere} films akin to '{movie}'?",
\item
"Have you seen '{movie}'? Any other {genere} movies to recommend?",
\item
"Looking for {genere} movies similar to '{movie}'? Let me know your favorites so far.",
\item
"Any {genere} films comparable to '{movie}' that you enjoyed recently?",
\item
"On the hunt for {genere} movies simillar to '{movie}'? Share your top picks.",
\item
"Recommendations for {genere} movies like '{movie}' would be great right now.",
\item
"Intrigued by '{movie}' lately? Discover more {genere} films with a similar feel.",
\item
"Excited to watch more {genere} movies like '{movie}'? Let's compile a watchlist.",
\item
"How about a movie night exploring '{movie}' and other {genere} films?",
\item
"Up for a discussion on hidden {genere} like '{movie}'?",
\item
"Curious about what makes '{movie}' special in the {genere} genre? Any Recommendation.",
\item
"Found any {genere} genre films like '{movie}' that left a lasting impression?",
\item
"Delving into the world of '{movie}' and {genere} movies. Got any favorites?",
\item
"Discovering movies similar to '{movie}' in the {genere} category is always a treat. Any suggestions?",
\item
"In the mood for {genere} films akin to '{movie}' tonight? Let's narrow down your options.",
\item
"Looking to broaden your movie horizon beyond '{movie}'? How about more {genere} films?",
\item
"Ready to expand your movie collection with {genere} movies like '{movie}'?",
\item
"What themes in '{movie}' resonate with you? Perhaps more {genere} genre films to explore.",
\item
"Planning your next movie marathon? Add some {genere} gems similar to '{movie}'.",
\item
"Enjoyed watching '{movie}'? Explore the {genere} genre for more hidden treasures.",
\item
"Can't get enough of {genere} films like '{movie}' after watching? Let's find more.",
\item
"Which {genere} movies have impressed you lately, following '{movie}'?",
\item
"Step into the world of '{movie}' and other {genere} films for a cinematic journey.",
\item
"On the lookout for {genere} movies with a similar impact to '{movie}'? Share your picks.",
\item
"Have a go at {genere} movies like '{movie}'. Found any standouts recently?",
\item
"Seeking out {genere} genre recommendations post-watching '{movie}'? Let's dive in.",
\item
"Fascinated by the storytelling in '{movie}' and {genere} movies. Any favorites to recommend?",
\item
"Looking to explore new {genere} films akin to '{movie}'? Count me in for recommendations.",
\item
"Ready to uncover more gems in the {genere} genre like '{movie}'? Let's build your watchlist.",
\item
"Inspired by the style of '{movie}' in the {genere} category? Discover more must-watch films.",
\item
"Any standout moments from '{movie}' or other {genere} films you'd like to explore further?",
\end{itemize}
\end{LTR}


همچنین در ادامه 50 قالب برای پاسخ آورده شده است.

\begin{LTR}
\begin{itemize}
\item
"Oh, you're into {genre} ? '{movie}' is a great pick! Have you seen '{similar\_movie}'? It's got a similar vibe but with some unexpected twists."
\item
"If you liked '{movie}', then you’ll probably enjoy '{similar\_movie}'. Both are solid {genre} films with killer soundtracks!"
\item
"Ah, {genre} movies like '{movie}' are my jam. If you want something lighter, check out '{similar\_movie}'."
\item
"'{movie}' was such a hit for me. For more {genre} goodness, I’d recommend '{similar\_movie}'—it’s underrated but amazing."
\item
"You’re spot-on about '{movie}' being an awesome {genre} film. Try '{similar\_movie}' next—it’s got the same emotional depth."
\item
"I’m obsessed with '{movie}'. Another {genre} flick that hits hard is '{similar\_movie}'. You won’t regret watching it!"
\item
"Great choice mentioning '{movie}'. If you’re craving more {genre} , give '{similar\_movie}' a shot. The visuals alone are worth it."
\item
"Yeah, '{movie}' nails the whole {genre} aesthetic. If you haven’t already, watch '{similar\_movie}'. It’s just as gripping."
\item
"Wow, we think alike! After '{movie}', I binged '{similar\_movie}'. Perfect for fans of {genre} stories."
\item
"Love how '{movie}' blends action and emotion. For another {genre} gem, try '{similar\_movie}'. Trust me, it’s binge-worthy."
\item
"If you’re digging {genre} stuff like '{movie}', you’ve gotta check out '{similar\_movie}'. It’s quirky but super relatable."
\item
"'{movie}' is iconic. If you’re looking for more {genre} vibes, '{similar\_movie}' will definitely scratch that itch."
\item
"Man, '{movie}' is timeless. If you’re up for another {genre} adventure, '{similar\_movie}' might be your new favorite."
\item
"For sure, '{movie}' is one of the best {genre} films ever. Pair it with '{similar\_movie}' for double the fun."
\item
"Love when people mention '{movie}'. If you’re hungry for more {genre} , '{similar\_movie}' delivers big time."
\item
"Totally agree about '{movie}'. For another {genre} powerhouse, go for '{similar\_movie}'. Same energy, different story."
\item
"I could rewatch '{movie}' a hundred times. For more {genre} magic, '{similar\_movie}' is where it’s at."
\item
"You picked a classic with '{movie}'. To keep the {genre} train rolling, add '{similar\_movie}' to your list."
\item
"Such a good call on '{movie}'. If you want more {genre} feels, '{similar\_movie}' is a must-watch."
\item
"I can’t get enough of '{movie}'. Another {genre} masterpiece is '{similar\_movie}'. Prepare to be blown away."
\item
"If '{movie}' spoke to you, '{similar\_movie}' will too. Both are {genre} classics with heartwarming moments."
\item
"Dude '{movie}' is perfection. For another dose of {genre} , '{similar\_movie}' is pure gold."
\item
"Can’t stop thinking about '{movie}'. If you need more {genre} inspiration, '{similar\_movie}' is a no-brainer."
\item
"Absolutely love '{movie}'. If you’re searching for more {genre} brilliance, '{similar\_movie}' is the answer."
\item
"That {genre} feeling from '{movie}' is unmatched. '{similar\_movie}' gives off the same cozy yet thrilling energy."
\item
"If you adore '{movie}', don’t sleep on '{similar\_movie}'. It’s another {genre} treasure waiting to be discovered."
\item
"So glad you brought up '{movie}'. For more {genre} awesomeness, '{similar\_movie}' is a game-changer."
\item
"Honestly, '{movie}' never gets old. If you’re jonesing for more {genre} , '{similar\_movie}' is a slam dunk."
\item
"The {genre} charm of '{movie}' is unbeatable. '{similar\_movie}' captures that same magic perfectly."
\item
"Yes, yes, YES to '{movie}'. For another {genre} knockout, '{similar\_movie}' is a guaranteed win."
\item
"Watching '{movie}' felt like therapy. For more {genre} comfort, '{similar\_movie}' is exactly what you need."
\item
"Who doesn’t love '{movie}'? If you’re hunting for more {genre} gems, '{similar\_movie}' is highly recommended."
\item
"Every time I watch '{movie}', I’m hooked. For more {genre} excellence, '{similar\_movie}' is a safe bet."
\item
"Definitely agree about '{movie}'. If you’re all about {genre} , '{similar\_movie}' should be next on your list."
\item
"The {genre} nostalgia from '{movie}' hits differently. '{similar\_movie}' brings back those same vibes effortlessly."
\item
"If '{movie}' made you smile, '{similar\_movie}' will too. Both are perfect {genre} escapes."
\item
"Couldn’t agree more about '{movie}'. For another {genre} standout, '{similar\_movie}' is a hidden gem."
\item
"Loving '{movie}' means you’ll probably adore '{similar\_movie}'. Both are top-tier {genre} picks."
\item
"There’s nothing like '{movie}' for {genre} lovers. Add '{similar\_movie}' to your queue—it’s equally captivating."
\item
"Big fan of '{movie}'. For more {genre} excitement, '{similar\_movie}' is a must-see."
\item
"The way '{movie}' balances humor and drama is genius. '{similar\_movie}' does the same for {genre} enthusiasts."
\item
"If '{movie}' resonated with you, '{similar\_movie}' will too. Both capture the essence of {genre} beautifully."
\item
"You nailed it with '{movie}'. For more {genre} brilliance, '{similar\_movie}' is a fantastic follow-up."
\item
"Absolutely crushing on '{movie}'. If you’re still vibing with {genre} , '{similar\_movie}' is a total winner."
\item
"The {genre} themes in '{movie}' are unforgettable. '{similar\_movie}' explores similar ideas in a fresh way."
\item
"I’m always recommending '{movie}'. For more {genre} greatness, '{similar\_movie}' is a certified banger."
\item
"There’s so much to love about '{movie}'. If you’re chasing more {genre} thrills, '{similar\_movie}' won’t disappoint."
\item
"'{movie}' is hands down one of the best {genre} films. '{similar\_movie}' holds its own alongside it."
\item
"Can’t say enough good things about '{movie}'. For another {genre} ride, '{similar\_movie}' is a stellar option."
\item
"You’re speaking my language with '{movie}'. If you’re ready for more {genre} , '{similar\_movie}' is calling your name."
\end{itemize}

\end{LTR}

